Analyses

### 2023-08-24 analyses.RmD
- shortened manuscript for submission

>>>>

# SESOI

In what follows, more information on how the SESOI was defined exactly.

If people can reliably differentiate 7 levels, this corresponds to 11 / 7 = `r round(11/7, 2)` unit change on an 11-point scale.
Hence, a four-point change in media use (e.g., a complete stop) should result in a `r round(11/7, 2)`-point change in life satisfaction.
In a statistical regression analysis, _b_ estimates the change in the dependent variable if the independent variable increases by one point.
For life satisfaction, we would therefore define a SESOI of _b_ = `r round(11/7, 2)` / 4 = `r round(11/7*.25, 2)`.
For positive or negative affect, which was measured on a 5-point scale, our SESOI would be _b_ = `r round(5 / 7, 2)` / 4 = `r round(5 / 7 * .25, 2)`.
Because we are agnostic as to whether the effects are positive or negative, the null region includes both negative and positive effects.
Finally, in order not to exaggerate precision and to be less conservative, these numbers are reduced to nearby thresholds.
Note that other researchers also decreased or recommended decreasing thresholds for effect sizes when analyzing within-person or cumulative effects [@beyensSocialMediaUse2021; @funderEvaluatingEffectSize2019].
